# Introduction {#intro}

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].

# Prerequisites

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

H~2~SO~4~

Fe^2+^

^137^~55~Cs

Blah <span style="font-variant:small-caps">Small Caps</span> blah

Blah <sc>Small Caps</sc> blah

$f(k) = {n \choose k} p^{k} (1-p)^{n-k}$

$$X = \begin{bmatrix}1 & x_{1}\\
1 & x_{2}\\
1 & x_{3}
\end{bmatrix}$$

\begin{equation} 
  f\left(k\right) = \binom{n}{k} p^k\left(1-p\right)^{n-k}
  (\#eq:binom)
\end{equation}

e.g., see Equation \@ref(eq:binom).

Un-numbered equation:

\begin{equation*} 
\frac{d}{dx}\left( \int_{a}^{x} f(u)\,du\right)=f(x)
\end{equation*}

A normal paragraph.

(ref:foo) A scatterplot of the data `cars` using **base** R graphics. 

```{r foo, fig.cap='(ref:foo)'}
plot(cars)  # a scatterplot
```

For now, you have to install the development versions of **bookdown** from Github:

```{r eval=FALSE}
devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need to install XeLaTeX.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

# Literature

Here is a review of existing methods.

# Methods

We describe our methods in this chapter.

# Applications

Some _significant_ applications are demonstrated in this chapter.

## Example one

## Example two

# Final Words

We have finished a nice book.

`r if (knitr:::is_html_output()) '# References {-}'`

## Notes

A many-way PAM partition of data for Acts 1-16 extracted from the apparatus of the UBS Greek New Testament (5th ed.) places 181 in a group with Psi, 614, Syr-p, Syr-h, and Old Church Slavonic. Syriac influence may be the common factor. (Concerning the Old Church Slavonic version, Crimea was once under the ecclesiastical jurisdiction of Antioch.[7]) 

[7] See Bruce M. Metzger, Early Versions of the New Testament (Oxford: Clarendon, 1977) p. 398.

```
rowSums(!is.na(read_data_frame("../Data/Acts.UBS5.csv")))

x = read_data_frame("../Data/Acts.UBS5.csv")

sum(!(is.na(x["L1178",])))

sum(!(is.na(x["Lect",])))
```
